\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
rearrange method

For comparative evaluation we used the gold standard dataset introduced by \citet{Yaminishi2008}, which includes both drug-target interaction pairs and side effects.\\

Eventually, we only considered proteins that had at least one link in either STITCH or STRING, and drugs with at least one side effect and one existing target. Thus, the intersection between these resources yielded 1160 drugs and 6680 human proteins for the training phase. We provide links to and methods for the necessary data in the provided Github repository.\\

>>>>

We only use proteins in our analysis that have at least one link in
either STITCH or STRING, and drugs with at least one side effect and
one existing target. Therefore, the intersection between these
resources yields 1,160 drugs and 6,680 human proteins for the training
phase. We provide links to and methods for obtaining and processing
the necessary data on Github.

For comparative evaluation, we use the gold standard dataset
introduced by \citet{Yaminishi2008} \todo[inline]{consisting of XXXX
  interactions between XXX drugs and XXX protein targets}.
